Differential invariant signatures for planar Lie group transformations of images

### 2020-08-21 paper/newpaper.tex
Relate MF and tensor invariants for E(2)

>>>>

These invariants are a functionally independent, complete, set of polynomial differential invariants up to second derivatives. Note that the invariants found previously by tensor contraction can be expressed in terms of these:
\begin{align*}
  f = f &= I_0 \\
  f_if_i = f_x^2 + f_y^2 &= I_1 \\
  f_{ii} = f_{xx}^2 + f_{yy}^2 &= \frac{I_2 + I_4}{I_1} \\
  f_{ij} f_{ij} = f_{xx}^2 + 2f_{xy}^2 + f_{yy}^2 &= I_2\\
  f_i f_j f_{ij} = f_x^2 f_{xx} + 2f_x f_y f_{xy} + f_y^2 f_{yy} &= \frac{I_2^2 + I_4^2 + 2I_3^2}{I_1^2}.
\end{align*}
